A meta-analysis of powdery mildew yield loss mitigation strategies in Australian mungbean

### 2021-03-03 index.Rmd
reduce title page

## Contents
This compendium is broken down into seven sections:

   1. [Details of the experiments, which were included in the analysis][Studies considered in meta-analysis]  
   2. [Preliminary data exploration which investigates possible variables that could influence the meta-analysis][Preliminary Analysis]  
      a. [Fungicides][Fungicides]  
      b. [Mungbean cultivar][Mungbean cultivars]  
      c. [Row spacing][Row spacing]  
      d. [Rainfall][Yield vs in-season rain]  
      e. [When conditions become suitable for powdery mildew infection][Season range and first incidence]  
   3. [Preparation of data for the meta-analysis][Prepare data for meta-analysis]  
   4. [Meta-analysis of the effect of fungicide spray schedule on yield loss][Meta-analysis]  
   5. [Meta-analysis of the effect of fungicide spray schedule on disease severity and yield loss][AUPDC meta-analysis]
   6. [Manuscript Wireframe][Manuscript wire frame]
   7. [Manuscript: A meta-analysis of fungicide use in mungbean to control for yield loss due to powdery mildew.][Manuscript]

## Other research questions, which are not the focus of this study

+ How has the first sign of powdery mildew changed between the seasons and experimental sites?

+ Is there an ideal planting time, or fungicide management strategy, which could make use of powdery mildew defoliation during pod maturation resulting in an increased yield?

+ Do infections that occur before flowering increase the probable yield loss?

## Possible sources of variation in this analysis.

+ Variability among host genotypes.

   + The probable influence of season might be influenced by host genotype.
   This is because newer varieties were adopted into experimental trials as they were released.

   + Between 2001 and 2015 mungbean genotype changed from Green Diamond, Berken, Crystal to Jade.
   Jade was the only cultivar used between 2015 and 2019.

   + Estimations of plant maturity stages over each growing season.
    These estimations might able to be computed using APSIM.

>>>>

## Contents
This compendium is broken down into four sections:

   1. [Details of the experiments, and application of inclusion criteria in the analysis][Trials considered for inclusion in meta-analysis]  
   2. [Preliminary data exploration][Preliminary Analysis]  
   *including a summary of the cleaned trial data and the treatments*
   3. [Grain yield meta-analysis]  
   4. [Powdery mildew severity Meta-analysis]

These sections detail the methods and process we undertook during this meta-analysis.

The manuscript publishing the results presented in this compendium can be found at ....

Preprint at .........
